---
title: "cvd4_further_analysis"
author: "Alice Dempsey"
date: "6/7/2021"
output: html_document
---
STEP ONE: Import and prep data for analysis
Import the cleanedData_cvd4 (from the cvd4 study -- interaction). Next, for each data set, copy the data from the csv to a data frame. Filter out corrupted data, ie nonsense answers or skipped sections. Filter out colorblind responses.

```{r import and prep}
library(lifecycle)
library(cli)
library(tidyverse)
library(ggplot2)
library(rcompanion)
library(rstatix)
library(BayesFactor)
library(dplyr)
library(freqtables)

cleanedData_cvd4 <- read_csv("cleanedData_cvd4.csv")
dfCvd4Data <- data.frame(cleanedData_cvd4[,1]) 
for (column in c(2:ncol(cleanedData_cvd4))){
  dfCvd4Data <- cbind(dfCvd4Data, cleanedData_cvd4[,column])
}
# drop people who skipped whole sections
dfCvd4Data <- subset(dfCvd4Data, dfCvd4Data$drop == 0)

# drop people who are colorblind or skipped that q
dfCvd4Data <- subset(dfCvd4Data, dfCvd4Data$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfCvd4Data <- subset(dfCvd4Data, (dfCvd4Data$ans1 > 0 & dfCvd4Data$ans1 <= 100))
dfCvd4Data <- subset(dfCvd4Data, !is.na(dfCvd4Data$ans1))
dfCvd4Data <- subset(dfCvd4Data, (dfCvd4Data$ans2 >= 0 & dfCvd4Data$ans2 <= 100))
dfCvd4Data <- subset(dfCvd4Data, !is.na(dfCvd4Data$ans2))

currCvd4Data <- data.frame("ID" = dfCvd4Data[,2], "stim" = dfCvd4Data[,4], "corr" = dfCvd4Data[,61], "spatial" = dfCvd4Data[,62])
```
```{r}
nrow(dfCvd4Data)
# str(currCvd4Data)

```

STEP TWO: How many individuals actually interacted? 

``` {r how many people interacted}
library(stringr)

people_interact <- subset(dfCvd4Data, dfCvd4Data$interacted == 1) 

#total number of people interacting
nrow(people_interact) 

both_checked <- data.frame("views" = dfCvd4Data[,12], "both" = 0)

for (row in 1:nrow(both_checked)) {
  if (length(grep("'you_test_cb': True", both_checked[row, 1])) > 0) {
    if (length(grep("'you_actual_cb': True", both_checked[row, 1])) > 0) {
      both_checked[row, 2] = 1
    }
  }
}

#number of people who check both boxes 
nrow(subset(both_checked, both_checked$both == 1))

#graph number of interactions by individual 
num_of_interactions <- str_count(both_checked$views, "\\{")

counts <- table(num_of_interactions)
barplot(counts, main="Number of Clicks (where 1 is the default -- no interaction)", xlab="Number of clicks", ylab="Number of individuals")

```

STEP THREE: Rerun basic analysis (ie graphing proportion of correct answers), filtering out those who got the ego-centric screening question wrong. 

```{r proportion by ego-centric question}

egoRightWrong <- data.frame(Study=character(), corr=integer())

#filtering data to keep those who got screening question 1 correct 
cvd4ego <- subset(dfCvd4Data, dfCvd4Data$ans01 == 'true positive')

egoRight <- data.frame("ID" = cvd4ego[,2], "stim" = cvd4ego[,4], "corr" = cvd4ego[,61], "spatial" = cvd4ego[,62])

print(nrow(egoRight))

#filtering data to keep those who got screening question 2 correct 
cvd4ego2 <- subset(dfCvd4Data, dfCvd4Data$ans02 == 'true positive')

egoRight2 <- data.frame("ID" = cvd4ego2[,2], "stim" = cvd4ego2[,4], "corr" = cvd4ego2[,61], "spatial" = cvd4ego2[,62])

print(nrow(egoRight2))

for(row in 1:nrow(egoRight)){
  temp <- data.frame("egoRight", egoRight[row, 3])
  names(temp) <- c("Study", "corr")
  egoRightWrong <- rbind(egoRightWrong, temp)
}

for(row in 1:nrow(egoRight2)){
  temp <- data.frame("egoRight2", egoRight2[row, 3])
  names(temp) <- c("Study", "corr")
  egoRightWrong <- rbind(egoRightWrong, temp)
}

for(row in 1:nrow(currCvd4Data)){
   temp <- data.frame("cvd4", currCvd4Data[row, 3])
  names(temp) <- c("Study", "corr")
  egoRightWrong <- rbind(egoRightWrong, temp)
}

#str(egoRightWrong)

egoRightWrongProp <- prop.test(x = c(sum(egoRight$corr), sum(currCvd4Data$corr)), n = c(nrow(egoRight), nrow(currCvd4Data)))
egoRightWrongProp

#plot 
plt <- egoRightWrong %>% 
  freq_table(Study, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$sa <- "egoRightWrong Data"


g <- ggplot(plt,aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))),
            color = "black", vjust=-1, size = 4) +
  labs(x = "Study", y = 'Proportion of Correct Answers') + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=1/3) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
g

```

STEP FOUR: Rerun analysis, filtering out people who did not interact 

```{r proportion by interacted or not}

interactedYesAll <- data.frame(Study=character(), corr=integer())

#filtering data to keep only those who interacted 
cvd4interacted <- subset(dfCvd4Data, dfCvd4Data$interacted == 1)

interacted <- data.frame("ID" = cvd4interacted[,2], "stim" = cvd4interacted[,4], "corr" = cvd4interacted[,61], "spatial" = cvd4interacted[,62])

for(row in 1:nrow(interacted)){
  temp <- data.frame("interacted", interacted[row, 3])
  names(temp) <- c("Study", "corr")
  interactedYesAll <- rbind(interactedYesAll, temp)
}

for(row in 1:nrow(currCvd4Data)){
   temp <- data.frame("cvd4", currCvd4Data[row, 3])
  names(temp) <- c("Study", "corr")
  interactedYesAll <- rbind(interactedYesAll, temp)
}

interactedYesAllProp <- prop.test(x = c(sum(interacted$corr), sum(currCvd4Data$corr)), n = c(nrow(interacted), nrow(currCvd4Data)))
interactedYesAllProp

#plot 
plt <- interactedYesAll %>% 
  freq_table(Study, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$sa <- "Interacted Data"


g <- ggplot(plt,aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))),
            color = "black", vjust=-1, size = 4) +
  labs(x = "Study", y = 'Proportion of Correct Answers') + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=1/3) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
g

```


STEP FIVE: Calculate error and graph it as a log regression 

``` {r error and log regression}
library(aod)
library(ggplot2)
library(e1071)

#summary(dfCvd4Data)

cvd4Error <- data.frame("ID" = dfCvd4Data[,2], "answer1" = dfCvd4Data[,10], "error1" = 0, "answer2" = dfCvd4Data[,11], "error2" = 0, "interactions" = dfCvd4Data[,"num_interactions"], "corr" = dfCvd4Data[,"corr"])

for (row in 1:nrow(cvd4Error)) {
  cvd4Error[row, "error1"] = (cvd4Error[row, "answer1"] - 57) / 57
  cvd4Error[row, "error2"] = (cvd4Error[row, "answer2"] - 56) / 56
}

par(mfrow=c(1, 2))  # divide graph area in 2 columns
plot(density(cvd4Error$error1), main="Density Plot: Error1", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(cvd4Error$error1), 2)))  
polygon(density(cvd4Error$error1), col="red")
plot(density(cvd4Error$error2), main="Density Plot: Error2", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(cvd4Error$error2), 2))) 
polygon(density(cvd4Error$error2), col="red")

# After looking at these ^^ graphs, I don't think that the error is normally distributed, so we can't do a linear regression ???  
linearMod <- lm(interactions ~ error1, data=cvd4Error)
print(linearMod)

corrlogit <- glm(corr ~ interactions, data = cvd4Error, family = "binomial")

summary(corrlogit)

wald.test(b = coef(corrlogit), Sigma = vcov(corrlogit), Terms = 1)

#exp(coef(corrlogit))

```


STEP SIX: Look for a relationship between whether an individual interacted and if they got the screening question correct 

``` {r interaction and screening question}

interactedScreening <- data.frame(Study=character(), corr=integer())

#filter for those who interacted 
cvd4interacted <- subset(dfCvd4Data, dfCvd4Data$interacted == 1)

interactedS <- data.frame("ID" = cvd4interacted[,2], "stim" = cvd4interacted[,4], "corr" = 0, "ans01" = cvd4interacted[,8])

cvd4S <- data.frame("ID" = dfCvd4Data[,2], "stim" = dfCvd4Data[,4], "corr" = 0, "ans01" = dfCvd4Data[,8])

#change the corr variable to be whether they got ans01 screening question right, not the numeric ans1 
for(row in 1:nrow(interactedS)){
  if (interactedS[row, "ans01"] == "true positive") {
    interactedS[row, "corr"] = 1
  }
  temp <- data.frame("interacted", interactedS[row, 3])
  names(temp) <- c("Study", "corr")
  interactedScreening <- rbind(interactedScreening, temp)
}

for(row in 1:nrow(cvd4S)){
  if (cvd4S[row, "ans01"] == "true positive") {
    cvd4S[row, "corr"] = 1
  }
  temp <- data.frame("cvd4", cvd4S[row, 3])
  names(temp) <- c("Study", "corr")
  interactedScreening <- rbind(interactedScreening, temp)
}

interactedScreeningProp <- prop.test(x = c(sum(interactedS$corr), sum(cvd4S$corr)), n = c(nrow(interactedS), nrow(cvd4S)))
interactedScreeningProp

#plot 
plt <- interactedScreening %>% 
  freq_table(Study, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$sa <- "Interacted Data"


g <- ggplot(plt,aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))),
            color = "black", vjust=-1, size = 4) +
  labs(x = "Study", y = 'Proportion of Correct Answers to Screening Q') + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=1/3) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
g




```
