---
title: "Cvd1 Study Results"
output:
  html_document:
    df_print: paged
---

## Data Cleaning 

```{r import and prep}
library(dplyr)
library(freqtables)
library(ggplot2)
library("gridExtra")  

# Define functions 
rbind.all.columns <- function(x, y) {
  x.diff <- setdiff(colnames(x), colnames(y))
  y.diff <- setdiff(colnames(y), colnames(x))
  x[, c(as.character(y.diff))] <- NA
  y[, c(as.character(x.diff))] <- NA
  return(rbind(x, y))
}

#set working directory for files
setwd("~/Documents/Documents - Ab’s MacBook Pro (3)/Research/covid_bayes")

#read in data
dfCvd1Data <- read.csv("cleanedData.csv") 

# drop people who skipped whole sections
dfCvd1Data <- subset(dfCvd1Data, dfCvd1Data$drop == 0)

# drop people who are colorblind or skipped that q
dfCvd1Data <- subset(dfCvd1Data, dfCvd1Data$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfCvd1Data <- subset(dfCvd1Data, (dfCvd1Data$ans1 > 0 & dfCvd1Data$ans1 <= 100))
dfCvd1Data <- subset(dfCvd1Data, !is.na(dfCvd1Data$ans1))
dfCvd1Data <- subset(dfCvd1Data, (dfCvd1Data$ans2 >= 0 & dfCvd1Data$ans2 <= 100))
dfCvd1Data <- subset(dfCvd1Data, !is.na(dfCvd1Data$ans2))

# add var for base vis
dfCvd1Data$base <- ifelse((dfCvd1Data$stim == "better" | 
                        dfCvd1Data$stim == 'betterStatic'), "grouped", 
                ifelse((dfCvd1Data$stim == "middle" | 
                          dfCvd1Data$stim == 'middleStatic'), "aligned", 
                  ifelse((dfCvd1Data$stim == "worse" | 
                            dfCvd1Data$stim == 'worseStatic'), "randomized",
                         "oops")))
dfCvd1Data$base <- as.factor(dfCvd1Data$base)
dfCvd1Data$base <- ordered(dfCvd1Data$base, levels = c("grouped", "aligned", "randomized"))
summary(dfCvd1Data$base)

# change time from milli-seconds to seconds
dfCvd1Data$time <- dfCvd1Data$time_diff_exp / 1000 
summary(dfCvd1Data$time)

# add scenario var
dfCvd1Data$scenario <- "COVID"

# read in Ab's interaction study data as base case  
dfBaseCase <- read.csv("cleanedData_pilot.csv")

# drop people who skipped whole sections
dfBaseCase <- subset(dfBaseCase, dfBaseCase$drop == 0)

# drop people who are colorblind or skipped that q
dfBaseCase <- subset(dfBaseCase, dfBaseCase$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfBaseCase <- subset(dfBaseCase, (dfBaseCase$ans1 > 0 & dfBaseCase$ans1 <= 100))
dfBaseCase <- subset(dfBaseCase, !is.na(dfBaseCase$ans1))
dfBaseCase <- subset(dfBaseCase, (dfBaseCase$ans2 >= 0 & dfBaseCase$ans2 <= 100))
dfBaseCase <- subset(dfBaseCase, !is.na(dfBaseCase$ans2))

# add var for interaction type and subset to static  
dfBaseCase$int <- ifelse((dfBaseCase$stim == 'better' | 
                              dfBaseCase$stim == 'middle' | 
                              dfBaseCase$stim == 'worse'), 'cbAll', 'static')
dfBaseCase <- subset(dfBaseCase, dfBaseCase$int == 'static')
dfBaseCase$int <- as.factor(dfBaseCase$int)

# add var for base vis
dfBaseCase$base <- ifelse((dfBaseCase$stim == "better" | 
                        dfBaseCase$stim == 'betterStatic'), "grouped", 
                ifelse((dfBaseCase$stim == "middle" | 
                          dfBaseCase$stim == 'middleStatic'), "aligned", 
                  ifelse((dfBaseCase$stim == "worse" | 
                            dfBaseCase$stim == 'worseStatic'), "randomized",
                         "oops")))
dfBaseCase$base <- as.factor(dfBaseCase$base)
dfBaseCase$base <- ordered(dfBaseCase$base, levels = c("grouped", "aligned", "randomized"))
summary(dfBaseCase$base)

# change time from milli-seconds to seconds
dfBaseCase$time <- dfBaseCase$time_diff_exp / 1000 
summary(dfBaseCase$time)

# add scenario var
dfBaseCase$scenario <- "Base Case Disease X"

```

## Is accuracy modulated by base visualization? 

Run a 2-sample test for equality of proportions of accuracy ~ base for the covid experiment and the original. We find no significant differences within either scenario.  

```{r accuracy_base}

# How does accuracy vary across base? 

# CVD
t_corr_by_bases_cvd <- xtabs( ~ base + corr, dfCvd1Data)
t_corr_by_bases_cvd

prop.test(t_corr_by_bases_cvd, alternative = "two.sided")

#orig
t_corr_by_bases_orig <- xtabs( ~ base + corr, dfBaseCase)
t_corr_by_bases_orig

prop.test(t_corr_by_bases_orig, alternative = "two.sided")

#plot 

# CVD
plt <- dfCvd1Data %>% 
  freq_table(base, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$row_cat <- ordered(plt$row_cat, levels = c("randomized", "aligned", "grouped"))
plt

g_cvd <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base", y = 'Proportion of Correct Answers',
       title = "COVID") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Set1")
#ggsave("e1_acc_by_bases.png")

# orig
plt <- dfBaseCase %>% 
  freq_table(base, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$row_cat <- ordered(plt$row_cat, levels = c("randomized", "aligned", "grouped"))
plt

g_orig <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base", y = 'Proportion of Correct Answers', 
       title = "Original") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Set1")
#ggsave("e1_acc_by_bases.png")

grid.arrange(g_cvd, g_orig, ncol = 1) 


```

## Is accuracy significantly different across scenarios? 

Run a 1-sample test for equality of proportions of accuracy ~ scenario for the combined data. 

```{r accuracy_scenario}

# How does accuracy vary across scenario? 

# combine datasets
df_combined <- rbind.all.columns(dfBaseCase, dfCvd1Data)

# prop test
t_corr_by_scenario <- xtabs( ~ scenario + corr, df_combined)
t_corr_by_scenario

prop.test(t_corr_by_scenario, alternative = "two.sided")

#plot 
plt <- df_combined %>% 
  freq_table(scenario, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt

g <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Scenario", y = 'Proportion of Correct Answers') + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
#ggsave("e1_acc_by_bases.png")
g

```

## Is accuracy significantly different across scenarios and bases? 

Run a 6-sample test for equality of proportions of accuracy ~ scenario X base.

```{r accuracy_base_scenario}

# Look for interaction between scenario and base 

#need counts of successes, and counts of trials 
all_corr <- subset(df_combined, df_combined$corr == 1)

t_succ <- xtabs( ~ base + scenario, all_corr)
t_succ
t_succ_v <- as.vector(t_succ)
t_succ_v

t_total <- xtabs( ~ base + scenario, df_combined)
t_total
t_total_v <- as.vector(t_total)
t_total_v

prop.test(t_succ_v, t_total_v, alternative = "two.sided")

#plot
t_succ_v <- as.data.frame(t_succ_v)
t_total_v <- as.data.frame(t_total_v)

cvd_grouped <- prop.test(t_succ_v[1,], t_total_v[1,], 
                           alternative = "two.sided")
cvd_aligned <- prop.test(t_succ_v[2,], t_total_v[2,], 
                           alternative = "two.sided")
cvd_randomized <- prop.test(t_succ_v[3,], t_total_v[3,], 
                              alternative ="two.sided")
orig_grouped <- prop.test(t_succ_v[4,], t_total_v[4,], 
                            alternative = "two.sided")
orig_aligned <- prop.test(t_succ_v[5,], t_total_v[5,], 
                            alternative = "two.sided")
orig_randomized <- prop.test(t_succ_v[6,], t_total_v[6,], 
                               alternative = "two.sided")
plt <- rbind(
c("COVID - grouped", "COVID", "grouped", cvd_grouped$estimate, 
  cvd_grouped$conf.int[1], cvd_grouped$conf.int[2]),
c("COVID - aligned", "COVID", "aligned", cvd_aligned$estimate, 
  cvd_aligned$conf.int[1], cvd_aligned$conf.int[2]),
c("COVID - randomized", "COVID", "randomized", cvd_randomized$estimate,
  cvd_randomized$conf.int[1], cvd_randomized$conf.int[2]),
c("Disease X - grouped", "Disease X", "grouped", orig_grouped$estimate, 
  orig_grouped$conf.int[1], orig_grouped$conf.int[2]),
c("Disease X - aligned", "Disease X", "aligned", orig_aligned$estimate, 
  orig_aligned$conf.int[1], orig_aligned$conf.int[2]),
c("Disease X - randomized","Disease X", "randomized", orig_randomized$estimate,
  orig_randomized$conf.int[1], orig_randomized$conf.int[2]))

colnames(plt) <- c("grp", "scenario", "base", "prop", "lcl", "ucl")
plt <- as.data.frame(plt)
plt$prop <- as.numeric(as.character(plt$prop))*100
plt$lcl <- as.numeric(as.character(plt$lcl))*100
plt$ucl <- as.numeric(as.character(plt$ucl))*100
plt$grp <- as.factor(plt$grp)
plt$grp <- ordered(plt$grp, 
                   levels = c("COVID - randomized",
                              "Disease X - randomized",
                              "COVID - aligned",
                              "Disease X - aligned", 
                              "COVID - grouped",
                              "Disease X - grouped"))
plt

g <- ggplot(plt, aes(x = grp, y = prop, 
               group = scenario, color = scenario)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl, ymax = ucl), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(prop, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base and Scenario", y = 'Proportion of Correct Answers') + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15)) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
g
#ggsave("e1_acc_by_bases_and_int.png")

```

## SA: Split data for SA analyses
```{r SA_split}
#split data into high and low SA
# Add spatial ability categories by splitting around median spatial ability score 

# CVD
m <- median(dfCvd1Data$spatialAbility, na.rm = TRUE)
m
r <- range(dfCvd1Data$spatialAbility, na.rm = TRUE)
r
dfCvd1Data$spatialHiLow <- ifelse(dfCvd1Data$spatialAbility >= m, "High", "Low")
dfCvd1Data$spatialHiLow <- as.factor(dfCvd1Data$spatialHiLow)
summary(dfCvd1Data$spatialHiLow)

dfCvd1Data_high <- subset(dfCvd1Data, dfCvd1Data$spatialHiLow == "High")
dfCvd1Data_low <- subset(dfCvd1Data, dfCvd1Data$spatialHiLow == "Low")

# orig
m <- median(dfBaseCase$spatialAbility, na.rm = TRUE)
m
r <- range(dfBaseCase$spatialAbility, na.rm = TRUE)
r
dfBaseCase$spatialHiLow <- ifelse(dfBaseCase$spatialAbility >= m, "High", "Low")
dfBaseCase$spatialHiLow <- as.factor(dfBaseCase$spatialHiLow)
summary(dfBaseCase$spatialHiLow)

dfBaseCase_high <- subset(dfBaseCase, dfBaseCase$spatialHiLow == "High")
dfBaseCase_low <- subset(dfBaseCase, dfBaseCase$spatialHiLow == "Low")

# combined
m <- median(df_combined$spatialAbility, na.rm = TRUE)
m
r <- range(df_combined$spatialAbility, na.rm = TRUE)
r
df_combined$spatialHiLow <- ifelse(df_combined$spatialAbility >= m, "High", "Low")
df_combined$spatialHiLow <- as.factor(df_combined$spatialHiLow)
summary(df_combined$spatialHiLow)

df_combined_high <- subset(df_combined, df_combined$spatialHiLow == "High")
df_combined_low <- subset(df_combined, df_combined$spatialHiLow == "Low")

```

## SA: Is accuracy modulated by base visualization? 

Run a 2-sample test for equality of proportions of accuracy ~ base for the covid experiment and the original within each SA. We find no significant differences within either scenario.  

```{r accuracy_base_SA}
# How does accuracy vary across base? 

# High 

# CVD
t_corr_by_bases_cvd <- xtabs( ~ base + corr, dfCvd1Data_high)
t_corr_by_bases_cvd

prop.test(t_corr_by_bases_cvd, alternative = "two.sided")

#orig
t_corr_by_bases_orig <- xtabs( ~ base + corr, dfBaseCase_high)
t_corr_by_bases_orig

prop.test(t_corr_by_bases_orig, alternative = "two.sided")

#plot 

# CVD
plt <- dfCvd1Data_high %>% 
  freq_table(base, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$row_cat <- ordered(plt$row_cat, levels = c("randomized", "aligned", "grouped"))
plt

g_cvd <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base", y = 'Proportion of Correct Answers',
       title = "COVID High SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Set1")
#ggsave("e1_acc_by_bases.png")

# orig
plt <- dfBaseCase_high %>% 
  freq_table(base, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$row_cat <- ordered(plt$row_cat, levels = c("randomized", "aligned", "grouped"))
plt

g_orig <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base", y = 'Proportion of Correct Answers', 
       title = "Original High SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Set1")
#ggsave("e1_acc_by_bases.png")

grid.arrange(g_cvd, g_orig, ncol = 1) 

# Low

# CVD
t_corr_by_bases_cvd <- xtabs( ~ base + corr, dfCvd1Data_low)
t_corr_by_bases_cvd

prop.test(t_corr_by_bases_cvd, alternative = "two.sided")

#orig
t_corr_by_bases_orig <- xtabs( ~ base + corr, dfBaseCase_low)
t_corr_by_bases_orig

prop.test(t_corr_by_bases_orig, alternative = "two.sided")

#plot 

# CVD
plt <- dfCvd1Data_low %>% 
  freq_table(base, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$row_cat <- ordered(plt$row_cat, levels = c("randomized", "aligned", "grouped"))
plt

g_cvd <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base", y = 'Proportion of Correct Answers',
       title = "COVID Low SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Set1")
#ggsave("e1_acc_by_bases.png")

# orig
plt <- dfBaseCase_low %>% 
  freq_table(base, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$row_cat <- ordered(plt$row_cat, levels = c("randomized", "aligned", "grouped"))
plt

g_orig <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base", y = 'Proportion of Correct Answers', 
       title = "Original Low SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Set1")
#ggsave("e1_acc_by_bases.png")

grid.arrange(g_cvd, g_orig, ncol = 1) 

```

## SA: Is accuracy significantly different across scenarios? 

Run a 1-sample test for equality of proportions of accuracy ~ scenario for the combined data across each SA. 

```{r accuracy_scenario_SA}

# How does accuracy vary across scenario? 

# High 

# prop test
t_corr_by_scenario <- xtabs( ~ scenario + corr, df_combined_high)
t_corr_by_scenario

prop.test(t_corr_by_scenario, alternative = "two.sided")

#plot 
plt <- df_combined_high %>% 
  freq_table(scenario, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt

g_high <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Scenario", y = 'Proportion of Correct Answers',
       title = "High SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
#ggsave("e1_acc_by_bases.png")

# Low 

# prop test
t_corr_by_scenario <- xtabs( ~ scenario + corr, df_combined_low)
t_corr_by_scenario

prop.test(t_corr_by_scenario, alternative = "two.sided")

#plot 
plt <- df_combined_low %>% 
  freq_table(scenario, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt

g_low <- ggplot(plt, aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Scenario", y = 'Proportion of Correct Answers',
       title = "Low SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
#ggsave("e1_acc_by_bases.png")

grid.arrange(g_high, g_low, ncol = 1)

```

## SA: Is accuracy significantly different across scenarios and bases? 

Run a 6-sample test for equality of proportions of accuracy ~ scenario X base for each SA.

```{r accuracy_base_scenario_SA}

# Look for interaction between scenario and base 

# High 

#need counts of successes, and counts of trials 
all_corr <- subset(df_combined_high, df_combined_high$corr == 1)

t_succ <- xtabs( ~ base + scenario, all_corr)
t_succ
t_succ_v <- as.vector(t_succ)
t_succ_v

t_total <- xtabs( ~ base + scenario, df_combined_high)
t_total
t_total_v <- as.vector(t_total)
t_total_v

prop.test(t_succ_v, t_total_v, alternative = "two.sided")

#plot
t_succ_v <- as.data.frame(t_succ_v)
t_total_v <- as.data.frame(t_total_v)

cvd_grouped <- prop.test(t_succ_v[1,], t_total_v[1,], 
                           alternative = "two.sided")
cvd_aligned <- prop.test(t_succ_v[2,], t_total_v[2,], 
                           alternative = "two.sided")
cvd_randomized <- prop.test(t_succ_v[3,], t_total_v[3,], 
                              alternative ="two.sided")
orig_grouped <- prop.test(t_succ_v[4,], t_total_v[4,], 
                            alternative = "two.sided")
orig_aligned <- prop.test(t_succ_v[5,], t_total_v[5,], 
                            alternative = "two.sided")
orig_randomized <- prop.test(t_succ_v[6,], t_total_v[6,], 
                               alternative = "two.sided")
plt <- rbind(
c("COVID - grouped", "COVID", "grouped", cvd_grouped$estimate, 
  cvd_grouped$conf.int[1], cvd_grouped$conf.int[2]),
c("COVID - aligned", "COVID", "aligned", cvd_aligned$estimate, 
  cvd_aligned$conf.int[1], cvd_aligned$conf.int[2]),
c("COVID - randomized", "COVID", "randomized", cvd_randomized$estimate,
  cvd_randomized$conf.int[1], cvd_randomized$conf.int[2]),
c("Disease X - grouped", "Disease X", "grouped", orig_grouped$estimate, 
  orig_grouped$conf.int[1], orig_grouped$conf.int[2]),
c("Disease X - aligned", "Disease X", "aligned", orig_aligned$estimate, 
  orig_aligned$conf.int[1], orig_aligned$conf.int[2]),
c("Disease X - randomized","Disease X", "randomized", orig_randomized$estimate,
  orig_randomized$conf.int[1], orig_randomized$conf.int[2]))

colnames(plt) <- c("grp", "scenario", "base", "prop", "lcl", "ucl")
plt <- as.data.frame(plt)
plt$prop <- as.numeric(as.character(plt$prop))*100
plt$lcl <- as.numeric(as.character(plt$lcl))*100
plt$ucl <- as.numeric(as.character(plt$ucl))*100
plt$grp <- as.factor(plt$grp)
plt$grp <- ordered(plt$grp, 
                   levels = c("COVID - randomized",
                              "Disease X - randomized",
                              "COVID - aligned",
                              "Disease X - aligned", 
                              "COVID - grouped",
                              "Disease X - grouped"))
plt

g_high <- ggplot(plt, aes(x = grp, y = prop, 
               group = scenario, color = scenario)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl, ymax = ucl), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(prop, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base and Scenario", y = 'Proportion of Correct Answers',
       title = "High SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15)) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
#ggsave("e1_acc_by_bases_and_int.png")

# Low 

#need counts of successes, and counts of trials 
all_corr <- subset(df_combined_low, df_combined_low$corr == 1)

t_succ <- xtabs( ~ base + scenario, all_corr)
t_succ
t_succ_v <- as.vector(t_succ)
t_succ_v

t_total <- xtabs( ~ base + scenario, df_combined_low)
t_total
t_total_v <- as.vector(t_total)
t_total_v

prop.test(t_succ_v, t_total_v, alternative = "two.sided")

#plot
t_succ_v <- as.data.frame(t_succ_v)
t_total_v <- as.data.frame(t_total_v)

cvd_grouped <- prop.test(t_succ_v[1,], t_total_v[1,], 
                           alternative = "two.sided")
cvd_aligned <- prop.test(t_succ_v[2,], t_total_v[2,], 
                           alternative = "two.sided")
cvd_randomized <- prop.test(t_succ_v[3,], t_total_v[3,], 
                              alternative ="two.sided")
orig_grouped <- prop.test(t_succ_v[4,], t_total_v[4,], 
                            alternative = "two.sided")
orig_aligned <- prop.test(t_succ_v[5,], t_total_v[5,], 
                            alternative = "two.sided")
orig_randomized <- prop.test(t_succ_v[6,], t_total_v[6,], 
                               alternative = "two.sided")
plt <- rbind(
c("COVID - grouped", "COVID", "grouped", cvd_grouped$estimate, 
  cvd_grouped$conf.int[1], cvd_grouped$conf.int[2]),
c("COVID - aligned", "COVID", "aligned", cvd_aligned$estimate, 
  cvd_aligned$conf.int[1], cvd_aligned$conf.int[2]),
c("COVID - randomized", "COVID", "randomized", cvd_randomized$estimate,
  cvd_randomized$conf.int[1], cvd_randomized$conf.int[2]),
c("Disease X - grouped", "Disease X", "grouped", orig_grouped$estimate, 
  orig_grouped$conf.int[1], orig_grouped$conf.int[2]),
c("Disease X - aligned", "Disease X", "aligned", orig_aligned$estimate, 
  orig_aligned$conf.int[1], orig_aligned$conf.int[2]),
c("Disease X - randomized","Disease X", "randomized", orig_randomized$estimate,
  orig_randomized$conf.int[1], orig_randomized$conf.int[2]))

colnames(plt) <- c("grp", "scenario", "base", "prop", "lcl", "ucl")
plt <- as.data.frame(plt)
plt$prop <- as.numeric(as.character(plt$prop))*100
plt$lcl <- as.numeric(as.character(plt$lcl))*100
plt$ucl <- as.numeric(as.character(plt$ucl))*100
plt$grp <- as.factor(plt$grp)
plt$grp <- ordered(plt$grp, 
                   levels = c("COVID - randomized",
                              "Disease X - randomized",
                              "COVID - aligned",
                              "Disease X - aligned", 
                              "COVID - grouped",
                              "Disease X - grouped"))
plt

g_low <- ggplot(plt, aes(x = grp, y = prop, 
               group = scenario, color = scenario)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl, ymax = ucl), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(prop, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Base and Scenario", y = 'Proportion of Correct Answers',
       title = "Low SA") + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15)) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
#ggsave("e1_acc_by_bases_and_int.png")

grid.arrange(g_high, g_low, ncol = 1)

```