---
title: "cvd3_cvd4_results"
output: html_notebook
---
STEP ONE: Import and prep data for analysis
Import the cleanedData_cvd3 (from the cvd3 study) and cleanedData_cvd4 (from cvd4 study) files. Next, for each data set, copy the data from the csv to a data frame. Filter out corrupted data, ie nonsense answers or skipped sections. Filter out colorblind responses. 

```{r import and prep}
library(lifecycle)
library(cli)

library(ggplot2)
library(rcompanion)
library(rstatix)
library(BayesFactor)
library(dplyr)
library(freqtables)

dfCvd3Data <- data.frame(cleanedData_cvd3[,1]) 
for (column in c(2:ncol(cleanedData_cvd3))){
  dfCvd3Data <- cbind(dfCvd3Data, cleanedData_cvd3[,column])
}
# drop people who skipped whole sections
dfCvd3Data <- subset(dfCvd3Data, dfCvd3Data$drop == 0)

# drop people who are colorblind or skipped that q
dfCvd3Data <- subset(dfCvd3Data, dfCvd3Data$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfCvd3Data <- subset(dfCvd3Data, (dfCvd3Data$ans1 > 0 & dfCvd3Data$ans1 <= 100))
dfCvd3Data <- subset(dfCvd3Data, !is.na(dfCvd3Data$ans1))
dfCvd3Data <- subset(dfCvd3Data, (dfCvd3Data$ans2 >= 0 & dfCvd3Data$ans2 <= 100))
dfCvd3Data <- subset(dfCvd3Data, !is.na(dfCvd3Data$ans2))

currCvd3Data <- data.frame("ID" = dfCvd3Data[,2], "stim" = dfCvd3Data[,4], "corr" = dfCvd3Data[,61], "spatial" = dfCvd3Data[,62])

str(currCvd3Data)

dfCvd4Data <- data.frame(cleanedData_cvd4[,1]) 
for (column in c(2:ncol(cleanedData_cvd4))){
  dfCvd4Data <- cbind(dfCvd4Data, cleanedData_cvd4[,column])
}
# drop people who skipped whole sections
dfCvd4Data <- subset(dfCvd4Data, dfCvd4Data$drop == 0)

# drop people who are colorblind or skipped that q
dfCvd4Data <- subset(dfCvd4Data, dfCvd4Data$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfCvd4Data <- subset(dfCvd4Data, (dfCvd4Data$ans1 > 0 & dfCvd4Data$ans1 <= 100))
dfCvd4Data <- subset(dfCvd4Data, !is.na(dfCvd4Data$ans1))
dfCvd4Data <- subset(dfCvd4Data, (dfCvd4Data$ans2 >= 0 & dfCvd4Data$ans2 <= 100))
dfCvd4Data <- subset(dfCvd4Data, !is.na(dfCvd4Data$ans2))

currCvd4Data <- data.frame("ID" = dfCvd4Data[,2], "stim" = dfCvd4Data[,4], "corr" = dfCvd4Data[,61], "spatial" = dfCvd4Data[,62])

str(currCvd4Data)

# Add in Cvd1 and Cvd2 data as well for comparisons 
dfCvd2Data <- data.frame(cleanedData_cvd2_pilot1[,1]) 
for (column in c(2:ncol(cleanedData_cvd2_pilot1))){
  dfCvd2Data <- cbind(dfCvd2Data, cleanedData_cvd2_pilot1[,column])
}
# drop people who skipped whole sections
dfCvd2Data <- subset(dfCvd2Data, dfCvd2Data$drop == 0)

# drop people who are colorblind or skipped that q
dfCvd2Data <- subset(dfCvd2Data, dfCvd2Data$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfCvd2Data <- subset(dfCvd2Data, (dfCvd2Data$ans1 > 0 & dfCvd2Data$ans1 <= 100))
dfCvd2Data <- subset(dfCvd2Data, !is.na(dfCvd2Data$ans1))
dfCvd2Data <- subset(dfCvd2Data, (dfCvd2Data$ans2 >= 0 & dfCvd2Data$ans2 <= 100))
dfCvd2Data <- subset(dfCvd2Data, !is.na(dfCvd2Data$ans2))

currCvd2Data <- data.frame("ID" = dfCvd2Data[,2], "stim" = dfCvd2Data[,4], "corr" = dfCvd2Data[,61], "spatial" = dfCvd2Data[,62])

str(currCvd2Data)

dfCvd1Data <- data.frame(cleanedData[,1]) 
for (column in c(2:ncol(cleanedData))){
  dfCvd1Data <- cbind(dfCvd1Data, cleanedData[,column])
}
# drop people who skipped whole sections
dfCvd1Data <- subset(dfCvd1Data, dfCvd1Data$drop == 0)

# drop people who are colorblind or skipped that q
dfCvd1Data <- subset(dfCvd1Data, dfCvd1Data$cb == 'not_colorblind')

# drop people who put in answers less than 1 or greater than 100, or NAN
dfCvd1Data <- subset(dfCvd1Data, (dfCvd1Data$ans1 > 0 & dfCvd1Data$ans1 <= 100))
dfCvd1Data <- subset(dfCvd1Data, !is.na(dfCvd1Data$ans1))
dfCvd1Data <- subset(dfCvd1Data, (dfCvd1Data$ans2 >= 0 & dfCvd1Data$ans2 <= 100))
dfCvd1Data <- subset(dfCvd1Data, !is.na(dfCvd1Data$ans2))

currCvd1Data <- data.frame("ID" = dfCvd1Data[,2], "stim" = dfCvd1Data[,4], "corr" = dfCvd1Data[,61], "spatial" = dfCvd1Data[,62])

str(currCvd1Data)

```


STEP TWO: Compare to cvd3 to cvd4  
Combine the Cvd3 study and the Cvd4 study results into one data frame, categorized by the study. Run proportion tests to compare the total number correct by study and graph the result. 

```{r proportion by study}

cvd3cvd4 <- data.frame(Study=character(), corr=integer())

for(row in 1:nrow(currCvd3Data)){
  temp <- data.frame("cvd3", currCvd3Data[row, 3])
  names(temp) <- c("Study", "corr")
  cvd3cvd4 <- rbind(cvd3cvd4, temp)
}

for(row in 1:nrow(currCvd4Data)){
   temp <- data.frame("cvd4", currCvd4Data[row, 3])
  names(temp) <- c("Study", "corr")
  cvd3cvd4 <- rbind(cvd3cvd4, temp)
}

#str(cvd3cvd4)

cvd3cvd4Prop <- prop.test(x = c(sum(currCvd3Data$corr), sum(currCvd4Data$corr)), n = c(nrow(currCvd3Data), nrow(currCvd4Data)))
cvd3cvd4Prop

# And do the same for Cvd1 and Cvd2 
cvd1Cvd2 <- data.frame(Study=character(), corr=integer())

for(row in 1:nrow(currCvd1Data)){
   temp <- data.frame("cvd1", currCvd1Data[row, 3])
  names(temp) <- c("Study", "corr")
  cvd1Cvd2 <- rbind(cvd1Cvd2, temp)
}

for(row in 1:nrow(currCvd2Data)){
  temp <- data.frame("cvd2", currCvd2Data[row, 3])
  names(temp) <- c("Study", "corr")
  cvd1Cvd2 <- rbind(cvd1Cvd2, temp)
}

#str(cvd1Cvd2)

cvd1Cvd2Prop <- prop.test(x = c(sum(currCvd2Data$corr), sum(currCvd1Data$corr)), n = c(nrow(currCvd2Data), nrow(currCvd1Data)))
cvd1Cvd2Prop

#plot 
plt <- cvd3cvd4 %>% 
  freq_table(Study, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$sa <- "Cvd3Cvd4 Data"

plth <- cvd1Cvd2 %>% 
  freq_table(Study, corr)

plth <- as.data.frame(plth)
plth <- subset(plth, plth$col_cat == 1)
plth$row_cat <- as.factor(plth$row_cat)
plth$sa <- "Cvd1Cvd2 Data"
plt <- rbind(plth, plt)


g <- ggplot(plt,aes(x = row_cat, y = percent_row, 
               group = row_cat, color = row_cat)) +
  ylim(0, 100) + 
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))),
            color = "black", vjust=-1, size = 4) +
  labs(x = "Study", y = 'Proportion of Correct Answers') + 
  theme_classic() + 
  theme(legend.position = "none", text = element_text(size=15),
        aspect.ratio=1/3) +
  coord_flip() + 
  scale_color_brewer(palette="Dark2")
g

```


STEP THREE: Compare between studies by visualization 
Sort both the Cvd3 study data and the Cvd4 study data by visualization type. Run proportion tests to compare the proportion of correct answers by visualization type by study. Graph the result. 

```{r proportion between studies by viz}

worseVizCvd3 <- data.frame()
middleVizCvd3 <- data.frame()
betterVizCvd3 <- data.frame()

for (row in 1:nrow(currCvd3Data)){
  if (currCvd3Data[row,2] == "worseStatic"){
    worseVizCvd3 <- rbind(worseVizCvd3, currCvd3Data[row,])
  }
  if (currCvd3Data[row,2] == "middleStatic"){
    middleVizCvd3 <- rbind(middleVizCvd3, currCvd3Data[row,])
  }
  if (currCvd3Data[row,2] == "betterStatic"){
    betterVizCvd3 <- rbind(betterVizCvd3, currCvd3Data[row,])
  }
}

worseVizCvd4 <- data.frame()
middleVizCvd4 <- data.frame()
betterVizCvd4 <- data.frame()

for (row in 1:nrow(currCvd4Data)){
  if (currCvd4Data[row,2] == "worseStatic"){
    worseVizCvd4 <- rbind(worseVizCvd4, currCvd4Data[row,])
  }
  if (currCvd4Data[row,2] == "middleStatic"){
    middleVizCvd4 <- rbind(middleVizCvd4, currCvd4Data[row,])
  }
  if (currCvd4Data[row,2] == "betterStatic"){
    betterVizCvd4 <- rbind(betterVizCvd4, currCvd4Data[row,])
  }
}

# worseStatic
worsecvd3cvd4 <- prop.test(x = c(sum(worseVizCvd3$corr), sum(worseVizCvd4$corr)), n = c(nrow(worseVizCvd3),  nrow(worseVizCvd4)))
worsecvd3cvd4

# middleStatic
middlecvd3cvd4 <- prop.test(x = c(sum(middleVizCvd3$corr), sum(middleVizCvd4$corr)), n = c(nrow(middleVizCvd3),  nrow(middleVizCvd4)))
middlecvd3cvd4

# betterStatic
bettercvd3cvd4 <- prop.test(x = c(sum(betterVizCvd3$corr), sum(betterVizCvd4$corr)), n = c(nrow(betterVizCvd3),  nrow(betterVizCvd4)))
bettercvd3cvd4

#plot
plt <- currCvd3Data %>%
  freq_table(stim, corr)

plth <- as.data.frame(plt)
plth <- subset(plth, plth$col_cat == 1)
plth$row_cat <- as.factor(plth$row_cat)
plth$sa <- "Cvd3 Data"

#plot
plt <- currCvd4Data %>% 
  freq_table(stim, corr)

plt <- as.data.frame(plt)
plt <- subset(plt, plt$col_cat == 1)
plt$row_cat <- as.factor(plt$row_cat)
plt$sa <- "Cvd4 Data"
plt <- rbind(plth, plt)

g <- ggplot(plt,aes(x = row_cat, y = percent_row, 
               group = sa, color = sa, shape = sa)) +
  ylim(0, 100) + 
  geom_errorbar(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_pointrange(aes(ymin = lcl_row, ymax = ucl_row), size = 1) +
  geom_text(aes(label=sprintf("%0.2f", round(percent_row, digits = 2))), 
            color = "black", vjust=-1, size = 4) +
  labs(x = "Viz Type", y = 'Proportion of Correct Answers') + 
  theme_classic() + 
  theme(legend.title=element_blank(), text = element_text(size=15),
        aspect.ratio=4/9) +
  coord_flip() + 
  scale_color_brewer(palette="Paired")
g


```